Was Devon Allen Unjustly Disqualified at the 2022 World Track and Field Championships?

### 2022-11-14 manuscript/manuscript.tex
Minor changes to intro section

The contribution of this paper is to question whether or not Seiko's timing data
was accurate and thus if Devon Allen was disqualified more so because of faulty
equipment rather than reacting illegally fast.  There is little at this point
that could be done to rectify any potential mis-qualification other than to try
to prevent it from happening again.

>>>>

The contribution of this paper is to question whether or not Seiko's timing data
was accurate and thus if Devon Allen was disqualified more so because of faulty
equipment rather than reacting illegally fast.  There is little at this point
that could be done to rectify any potential mis-qualification other than to try
to prevent it from happening again. Devon Allen's disqulification needs to be
addressed because this is a problem that could continue to re-appear.  If athletes
are reacting fast enough that the timing system thinks that they are reacting
illegally fast, then World Athletics needs to address this and possibly change
the minimum reaction time allowed.  Other papers have discussed track and field
reaction times but not in the context of whether the minimum reaction time barrier
is too low or whether or not timing systems were at fault.
